---
title: '19583_loot Report'
date: '`r Sys.Date()`'
output:
    html_document:
    toc: TRUE
    toc_float: TRUE
params:
  nb_input: -1
---

\n\n<br /><br />\n\n




[comment]: <> (The following script is used to be able to zoom on images)

<script>
  function toggleFullscreen(img) {
    if (img.classList.contains('fullscreen')) {
      img.classList.remove('fullscreen');
    } else {
      document.querySelectorAll('.fullscreen').forEach(el => el.classList.remove('fullscreen'));
      img.classList.add('fullscreen');
    }
  }
</script>
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>Images cliquables</title>
    <style>
        .image-container {
            display: flex;
            justify-content: space-around;
            gap: 10px;
        }
        .image-container img {
            width: 33%;
            cursor: pointer;
            transition: transform 0.3s ease;
        }
        .fullscreen {
            position: fixed;
            top: 0;
            left: 0;
            width: 100vw !important;
            height: 100vh !important;
            object-fit: contain;
            background: rgba(0, 0, 0, 0.9);
            z-index: 1000;
            transform: scale(1);
        }
    </style>
</head>

[comment]: <> (End of script to zoom on images)

[comment]: <> (The following script is meant to display the tsvs in a readable way)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(knitr)

read_tsv_with_dummy <- function(file_path) {
  if (file.info(file_path)$size == 0) {
    return("File is empty")
  } else {
    df <- read_tsv(file_path, show_col_types = FALSE)
    truncated <- FALSE
    # If the file is empty but has column names, add an empty line to make the column names readable
    if (nrow(df) == 0) {
      dummy_row <- as.data.frame(matrix("", nrow = 1, ncol = ncol(df)))
      colnames(dummy_row) <- colnames(df)
      df <- rbind(df, dummy_row)
    }else if (nrow(df) > 10) {
      df <- df[1:10, ]
      truncated <- TRUE
    }
    attr(df, "truncated") <- truncated
    return(df)
  }
}
```

<style>
details.inline {display:inline-block;}
</style>

[comment]: <> (End tsv display)



### Initial dataset

Number of initial input files : ```r params$nb_input```

<br><br>

### MultiQC

Results are published in the [Report](./reports/multiqc_report.html) folder

<br><br>

###  Backup


See the [reports](./reports) folder for all the details of the analysis, including the parameters used in the .config file.
```{r include = FALSE}
#remove work directory from current directory
wd <- getwd()
parts <- unlist(strsplit(wd, "/"))
path <- paste(parts[1:(length(parts) - 3)], collapse = "/")
path <- paste0(path, "/")
```
Warning: the full .nextflow.log is in: ```r path```. Indeed, the one in the [reports](./reports) folder is not complete (miss the end).


<br /><br />

<style>
  #TOC { max-width: 200px !important;}
  /* .tocify-item { font-size: 100% !important; } */
</style>

<style> 
  body .container, body .container-fluid { max-width: 90% !important; width: 100% !important; margin: 0 auto;  } 
</style>

<style>
  .toc-content.col-xs-12.col-sm-8.col-md-9 { margin-left: 10px !important; padding-left: 0 !important; } 
</style>

<style> /* Force a fixated width, float left and add space on the right */ .col-xs-12.col-sm-4.col-md-3 { width: 250px !important; float: left; margin-right: 20px; /* reduce interior margin */ padding: 5px; } </style>
